### 2023-10-20 vesicle_code/docs/confinedMulti/response.tex

\begin{enumerate}
%%%%%%%%
\item The authors specify a line energy parameter $\epsilon = 100$. It
  is important that the authors justify this choice along with an
    experimental study which uses similar parameter ranges. This is
    important so that a future experimental study could be performed
    using these parameters as a guide.

\noindent
{\bf Response:} This was a typo. We checked our code, and now we
report the correct value in the revision which is $\epsilon = 0.04$.
This value corresponds to a transition region of size $10^{-1}$ microns
between stiff and floppy regions. Comparable values are used in the
literature, and we cite three of these papers.

%%%%%%%%
\item Minor comment: In Figure 4 and 5, the authors should add the $x$
  coordinate under the figure so that the readers are able to understand
    the results better.

\noindent
{\bf Response:} Thank you for the suggestion. The $x$ coordinate is
added to these figures in the revised manuscript.

@@

\noindent
    {\bf Response:} We calculated the tangential velocity of all $N =
    1024$ Lagrangian points for each of the three cases. Plotting all
    1024 lines in the manuscript would be uninformative. To prove this is
    the case, a plot of 32 of the tangential velocities is in Figure~\ref{fig:tangVel} of this document. 
%    
Instead we track the tangential velocity of each Lagrangian marker on
the vesicle membrane, measuring the spread in this tangential velocity
over the part of the period when the vesicle is inside the stenosis.
This spread, scaled by the velocity magnitude, is color-coded along the
membrane and is now part of Figure 7. The original plots showing the
tangential velocity of the four points are removed. For a tank-treading
vesicle, this scheme would give a membrane of a uniform color. On the
other hand, a non-uniformly colored membrane implicates the lack of
tank-treading in the vesicle membrane, which may also correspond to
significant deformations in the membrane.
%   
% Instead, in the document,
%  we report the average tangential velocity in the region $x \in
% [4,10]$, and report the spread of all tangential velocities from
%this mean value. 
More quantitatively, if this spread is less than 15\%, we would
characterize this as a tank-treading vesicle. Their spread is 1.2\% for
the stiff single-component vesicle, 12\% for the multicomponent case,
and 313\% for the floppy single-component case. Therefore, the floppy
single-component vesicle is not tank-treading, while the other two cases
are tank-treading. We have made this clear in the text.

\begin{figure}[ht]
  \centering
  \subfigimg[width=0.3\textwidth]{(a)}{figures/SC_treading_velocity_review.pdf}
  \subfigimg[width=0.3\textwidth]{(b)}{figures/SCp55_treading_velocity_review.pdf}
  \subfigimg[width=0.3\textwidth]{(c)}{figures/MCp5_treading_velocity_review.pdf}
  \caption{\label{fig:tangVel} \small The tangential velocity of 32
  points of the (a) stiff single-component vesicle, (b) floppy
  single-component vesicle, (c) multicomponent vesicle. Note that these
  figures, and the version with four marker points, are excluded from
  the revised manuscript.}
\end{figure}

@@

%%%%%%%%
\item In Figure 6, the author should comment on the energy behavior of
  the floppy vesicle in the stenosis region.

\noindent
{\bf Response:} We have included a discussion of the energy behavior of
the floppy vesicle and compared it with the stiff case.

%%%%%%%%
\item In Figure 7, when the authors look at the excess pressure plots,
  they should describe the behavior of the floppy vesicle due to the
  difference in lubrication thickness and, in turn, excess pressure. It
  seems like the excess pressure shows a similar trend as the stiff
  vesicle.

\noindent
{\bf Response:} In the original submission, we attempted to relate the
excess pressure to the lubrication layer thickness. However, as pointed
out by the reviewer, we did not make any reference to the floppy case.
As a general trend, the sum of the top and bottom lubrication layer
thicknesses is correlated with the magnitude of the excess
pressure---larger lubrication layers correspond to smaller (less
negative) excess pressures. This is because smaller excess pressure is
required to push the same amount of fluid around the vesicle when the
lubrication layer thickness is larger. The text has been adjusted.

@@

\begin{enumerate}
%%%%%%%%
\item This study is limited to the two-dimensional case, which is not
  reality. It is a strong approximation and full 3D studies are still a
    challenge in constrictions. But, in the axisymmetrical case, there
    are several results in literature which could be more or less,
    considered as benchmark:
    \url{http://dx.doi.org/10.1103/PhysRevFluids.5.043602}, \\
    \url{https://doi.org/10.1017/jfm.2017.743}

\noindent
{\bf Response:} Thank you for the comment. It is addressed in detail in
our response to the reviewer's second comment.

%%%%%%%%
\item The authors should justify why they limit their investigations to
  the 2D case if 3D is possible. I note that the authors also cite
    relevant literature as 10, 11 $\ldots$ References to 2D are
    excellent. A typical argument is the high time of 3D simulations.
    Can the authors provide an order of magnitude?

\noindent
{\bf Response:} There is published work that investigates elements of
our work in  3D. This includes the papers from the reviewers first
comment that consider vesicles in strong confinement, but these works
assume axisymmetry and neither consider multicomponent vesicles. Two 3D
works that relax the axisymmetric assumption and simulate vesicles in
strong confinement are also cited in the original submission
(\url{https://doi.org/10.1063/1.5081057} and
\url{https://doi.org/10.1103/PhysRevFluids.5.013603}). Red blood cells
undergoing strong confinement has also been considered using other
numerical methods including a spring model coupled to smoothed particle
hydrodynamics (\url{http://dx.doi.org/10.1016/j.taml.2015.11.006} and
\url{http://dx.doi.org/10.1063/1.4817959}). These papers are cited in
the revised manuscript.

There is much less work on 3D multicomponent vesicles. Phase field
models are used by Wang and Du
(\url{https://doi.org/10.1007/s00285-007-0118-2}) and a level set method
is used by Gera and Salac
(\url{https://doi.org/10.1016/j.compfluid.2018.04.003}). The challenge
with both these approaches is that they discretize the fluid volume, and
this limits how small $\epsilon$ can be, and therefore restricts the
sharpness of the transition between the floppy and stiff regions. In
both these works, a value of $\epsilon$ is used that is at least
ten-times larger than the more realistic value used in our work. To use
a comparable value to ours, they would have to increase the overall
spatial resolution by $10^3$. These codes are parallelized and highly
optimized, but they still take on the order of a day to complete one
unconfined simulation at the coarser resolution. Therefore, with
confinement, and the additional resolution to resolve the more physical
value of $\epsilon$, a single simulation would require much more
computational resources to generate an appropriately large dataset to
analyze. For example, if a simulation for an unconfined case requires
one day of wall clock time on 12 cores, then, even without confinement,
the additional resolution required to resolve the smaller value of
$\epsilon$ would require 12,000 cores to complete the simulation in the
same wall clock time, and this is assuming the code scales perfectly.
This increase in resources would be compounded further once strong
confinement is introduced.

Extending our 2D spectral code to 3D is challenging because resolving
the sharp interface between lipid domains requires special treatment
such as adaptive methods. Recently, finite element methods with adaptive
mesh generation have been used to solve surface PDEs, but to our
knowledge, it has not been extended to fourth-order PDEs or evolving
surfaces (as in our case). For example, see the following thesis that
considers reaction-diffusion systems on surfaces
(\url{https://nrs.harvard.edu/URN-3:HUL.INSTREPOS:37368862}), and the
preprint written by the same author
(\url{https://arxiv.org/pdf/2210.00022.pdf}). Extending this work to
incorporate a high-order phase field model and deformable interface is
currently unavailable, to the best of our knowledge.

@@

%%%%%%%%
\item The authors present the essential steps of the numerical model. It
  is well done and the references well chosen. I have appreciated the
    introduction of equation (9) an figure 2. However, there are two
    points to clarify :
    \begin{itemize}
      \item page 2: there is a difference in literature of the
        capillary number. Some authors use the flow curvature, others
        the mean velocity as the authors. Please explain your choice.
      \item page 2, right column ``The parameter $\epsilon \ll 1$ sets
        the size of the transition region of u, and the parameter a is
        line tension scaled by the characteristic bending stiffness. All
        simulations use the parameter values $\epsilon = 100$ and $a =
        0.04.$" $\epsilon = 100$ is contradictory to $\epsilon \ll 1$.
        Please explain or correct
    \end{itemize}

\noindent
{\bf Response:} We use the maximum imposed velocity to define the
capillary number so that we can compare our results with work that we
cite including [10,11,18] (as numbered in our original submission). We
have also added a note that the capillary number is larger when a
vesicle is inside the stenosis.

For the comment regarding the value of $\epsilon$, we had a typo. We
have checked our code, and the parameter value for $\epsilon$ is
actually 0.04. This has been fixed in the revised manuscript.

@@

%%%%%%%%
\item Why do authors never observe the blocking of vesicles contrary to
  experiments? It would the opportunity to perform a phase diagram and
    to show the effect of multicomponent.

\noindent
{\bf Response:} We initially explored cases where the single-component
vesicle became stuck, expecting that the multicomponent vesicle may pass
through the same geometry. We did not find any such cases.
However, we did observe other behaviors that differ between the two
cases, including the vesicle shape, tank-treading velocity, lubrication
layer, and these comparisons are the focus of our manuscript. We defer
our response to the phase diagram point until comment number 6.

@@

%

%%%%%%%%
\item In experiments, the channel is a slit. What do the authors expect
  from such a difference?

\noindent
{\bf Response:} We are interpreting this question as the reviewer asking
about 3D effects. In the literature, the 3D simulations of a red blood
cell through a 3D slit (see Lu and Peng,
\url{https://doi.org/10.1063/1.5081057}) has a 2D projection that looks
similar to our 2D simulations. In particular their right-most panel in
Figure 5(b) resembles Figures 10(d) and 10(e) in columns V and VI in our
manuscript. Other than the shape similarity of the 2D projection, we
also find that our excess pressure is of the same order for a similar
flow rate in a 3D case (\url{http://dx.doi.org/10.1063/1.4817959}).

@@

%%%%%%%%
\item Finally, this study is interesting and provides new insights.
  However, I advise authors to improve the quantitative part of their
  results (variation with Ca or confinement or something else, phase
  diagram...) to be more relevant for a journal such as Soft Matter. I
  am waiting the new manuscript.

\noindent
{\bf Response:} Agarwal and Biros
(\url{http://www.doi.org/10.1103/PhysRevFluids.5.013603})  recently
showed that when a vesicle is in a channel with strong confinement,
there are at most two different shapes a vesicle can take on for
different capillary numbers (see Figure 18a). They observe this for
confinement ratios as large as 0.7, and our examples have a confinement
ratio closer to 2 (stronger confinement). At such strong confinement, we
do not expect the capillary number to have an effect on the vesicle
  shape. To substantiate this claim, we consider a single multicomponent
  vesicle in an unconfined non-linear shear flow at various capillary
  numbers and reduced areas. The phase diagram (Figure~\ref{fig:Phase})
  shows that the multicomponent vesicle is more symmetric in shape than
  the single-component vesicle for a wide range of capillary numbers and
  reduced areas. Based on this, we speculate that a phase diagram with
  strong confinement would be less interesting than the single-component
  case, so we exclude a phase diagram with confinement.

We have also discussed this topic with a colleague who works on
experiments with red blood cells forming a single line along the
mid-plane as they pass through stenosis. His experiments show that the
shape of the red blood cell inside this confined stenosis is independent
over a range of capillary numbers. For this reason, we focus on the
relationships between between the vesicle shape, lubrication layer,
excess pressure, and asymmetry relative to the midline.

We have started examining the dependence of the vesicle symmetry on
other dimensionless parameters such as the confinement ratio and the
floppy-to-stiff ratio. This will likely give rise to different phenomena
and analyses that would distract from the focus of this work.
\begin{figure}
\centering
  \includegraphics[width=0.5\textwidth]{phaseDiagram.pdf}
  \caption{\label{fig:Phase} \small A phase diagram of a single
  multicomponent vesicle in an unconfined nonlinear shear flow. The
  capillary number has no effect on the steady state shape of the
  vesicle.}
\end{figure}

### 2023-10-20 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
last few changes ... I hope

\begin{figure*}[ht]
  \centering
  \subfigimg[width=0.3\linewidth]{(a)}{figures/SC_energy.pdf}
  \subfigimg[width=0.3\linewidth]{(b)}{figures/SCp55_energy.pdf}
  \subfigimg[width=0.3\linewidth]{(c)}{figures/MCp5_energy.pdf}
  \caption{\label{fig:Energy} \small The bending (blue), tension (red),
  and phase (green) energies of a (a) stiff single-component, (b)
  floppy single-component, and (c) multicomponent vesicle. The reduced
  area is $\alpha = 0.4$. Note that the single-component vesicles do not
  have a phase energy.} 
\end{figure*}
\begin{figure*}[ht]
  \centering
  \subfigimg[width=0.3\linewidth]{(a)}{figures/Layer_Size_RAp4_SC.pdf}
  \subfigimg[width=0.3\linewidth]{(b)}{figures/Layer_Size_RAp4_SCp55.pdf}
  \subfigimg[width=0.3\linewidth]{(c)}{figures/Layer_Size_RAp4_MCp5.pdf}
  \subfigimg[width=0.3\linewidth,trim=4cm 20cm 33cm 7cm,clip=true]{}
    {figures/SC_treading_velocity2.pdf}
  \subfigimg[width=0.3\linewidth,trim=4cm 20cm 33cm 7cm,clip=true]{}
    {figures/SCp55_treading_velocity2.pdf}
  \subfigimg[width=0.3\linewidth,trim=4cm 20cm 33cm 7cm,clip=true]{}
    {figures/MCp5_treading_velocity2.pdf}
%  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm 0cm,clip=true]{}{figures/TankTreadingFigs_composite_SC.pdf}
%  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
%  0cm,clip=true]{}{figures/TankTreadingFigs_composite_SCp55.pdf}
%  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
%  0cm,clip=true]{}{figures/TankTreadingFigs_composite_MCp5.pdf}
  \caption{\label{fig:lubricationComposite} \small The lubrication layer
  thicknesses (red and blue), excess pressure (green), and
  tank-treading velocity of four Lagrangian points of a (a) stiff
  single-component vesicle, (b) floppy single-component vesicle, and (c)
  multicomponent vesicle. The reduced area is $\alpha = 0.4$ in all
  three cases. 
  \textcolor{blue}{
  Also illustrated is the vesicle shape when its center of mass is
  located at $x=4$. Then, color represents the spread of the tangential
  velocity relative to the average tangential velocity, where the average
  is taken over the region $x \in [4,10]$. We characterize the stiff
  single-component and multicomponent vesicles as tank treading since
  the spread in the tangential velocity is below 15\%, while the floppy
  single-component vesicle is not tank treading.
  }
%  Also illustrated is the vesicle shape and the four
%  Lagrangian points at the location indicated by the dash line.
  The black dashed line is the center line of the channel, and the arrow
  denotes the tank-treading direction. The percentage of the vesicle
  membrane that is below the center line is (a) 72\%, (b) 44\%, and (c)
  68\%.}
\end{figure*}

@@

Another difference between the two reduced areas is that the vesicles
with smaller reduced area undergo tank-treading motions. As mentioned
earlier, tank-treading occurs when the top and bottom lubrication layers
differ in size. The size of the lubrication layers for all three cases
of the vesicle with reduced area $\alpha = 0.4$ are in the top half of
Figure~\ref{fig:lubricationComposite}. 
%The bottom of Figure~\ref{fig:lubricationComposite} shows the
%tank-treading velocities of four Lagrangian points. The inset shows the
%vesicle configuration in the closely-fitting part of the channel, the
%black dashed line is the center line of the channel, the marks are the
%four Lagrangian points, and the rounded arrow denotes the direction of
%rotation. 
\textcolor{blue}
{
To determine if a vesicle is tank-treading, we first calculate the
average, maximum, and minimum tangential velocities over all $N$
Lagrangian points when the vesicle's center of mass is in the interval
$[4,10]$. If the difference of the maximum and minimum tangential
velocities is within 15\% of the average tangential velocity, we
characterize the vesicle as tank-treading. These relative relative
spreads are plotted in the bottom row of
Figure~\ref{fig:lubricationComposite}. The average tangential velocities
are $-1.00 \times 10^{-1}$ for the stiff single-component vesicle, $3.31
\times 10^{-2}$ for the floppy single-component vesicle, and $-8.48
\times 10^{-1}$ for the multicomponent vesicle. The difference of the
maximum and minimum velocities relative to the average tangential
velocities is $1.2\%$ for the stiff single-component vesicle, $12\%$ for
the multicomponent vesicle, and over $300\%$ for the floppy
single-component vesicle. Therefore, we classify the stiff
single-component and multicomponent vesicles as tank treading, while the
floppy single-component is not tank treading.}
%The stiff single-component and multicomponent vesicles are
%clearly tank treading.
The direction and speed of the tank-treading depends on how much of the
vesicle membrane is exposed to positive shear (below the center line)
versus how much is exposed to negative shear (above the center
line)~\cite{kao-bir-mis2009}. The majority of the membrane of the stiff
single-component and multicomponent vesicles are below the center line,
and this results in a clockwise tank-treading behavior. In contrast, the
majority of the membrane of the floppy single-component vesicle is above
the center line, and the result is counterclockwise 
\textcolor{blue}{
rotation, but, again, large normal defomrations are occuring along with
the rotation.
%}
%tank-treading. 
%\textcolor{blue}{
Finally, the stiff single-component vesicle tank treads faster than the
multicomponent cases since more of its membrane is located below the
center line.
}
%In addition, the tank-treading velocity can be correlated to the
%percentage of its membrane that is below the center line. 
%We note, however, that the floppy single-component vesicle is still
%undergoing deformations, so the tangential velocities have not converged
%to a fixed value.

The sizes of the top and bottom lubrication layers are also related to
the excess pressure. The green curve on the top half of
Figure~\ref{fig:lubricationComposite} shows the excess pressure (with
the axis aligned on the right side of the plot). 
\textcolor{blue}{
As a general trend, we find that the sum of the top and bottom
lubrication layer thicknesses is correlated with the magnitude of the
excess pressure---larger lubrication layers correspond to smaller (less
negative) excess pressures. This is because smaller excess pressure is
required to push the same amount of fluid around the vesicle when the
lubrication layer thickness is larger.}
%As a general trend, we expect that if the total lubrication layer
%thickness---namely the sum of the top and bottom lubrication layers---is
%largest, then less pressure is required to maintain the constant flow
%rate, and the result is a smaller (less negative) excess pressure. This
%trend is confirmed in Figure~\ref{fig:lubricationComposite} where the
%size of the lubrication layers, from smallest to largest, are the stiff
%single-component vesicle, the floppy single-component vesicle, and the
%multicomponent vesicle, while the ranking of the excess pressure is
%reversed.}
%When the lubrication layers are large, most notably for the
%multicomponent vesicle, less pressure is required to force the vesicle
%through the geometry, and the result is a smaller (less negative)
%excess pressure. In contrast, when the lubrication layers are small,
%most notably for the stiff single-component vesicle, more pressure is
%required to force the vesicle through the geometry, and we the result
%is a larger (more negative) excess pressure.

>>>>

\begin{figure*}[ht]
  \centering
  \subfigimg[width=0.3\linewidth]{(a)}{figures/SC_energy.pdf}
  \subfigimg[width=0.3\linewidth]{(b)}{figures/SCp55_energy.pdf}
  \subfigimg[width=0.3\linewidth]{(c)}{figures/MCp5_energy.pdf}
  \caption{\label{fig:Energy} \small The bending (blue), tension (red),
  and phase (green) energies of a (a) stiff single-component, (b)
  floppy single-component, and (c) multicomponent vesicle. The reduced
  area is $\alpha = 0.4$. Note that the single-component vesicles do not
  have a phase energy.} 
\end{figure*}
\begin{figure*}[ht]
  \centering
  \subfigimg[width=0.3\linewidth]{(a)}{figures/Layer_Size_RAp4_SC.pdf}
  \subfigimg[width=0.3\linewidth]{(b)}{figures/Layer_Size_RAp4_SCp55.pdf}
  \subfigimg[width=0.3\linewidth]{(c)}{figures/Layer_Size_RAp4_MCp5.pdf}
  \subfigimg[width=0.3\linewidth,trim=4cm 20cm 33cm 7cm,clip=true]{}
    {figures/SC_treading_velocity2.pdf}
  \subfigimg[width=0.3\linewidth,trim=4cm 20cm 33cm 7cm,clip=true]{}
    {figures/SCp55_treading_velocity2.pdf}
  \subfigimg[width=0.3\linewidth,trim=4cm 20cm 33cm 7cm,clip=true]{}
    {figures/MCp5_treading_velocity2.pdf}
%  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm 0cm,clip=true]{}{figures/TankTreadingFigs_composite_SC.pdf}
%  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
%  0cm,clip=true]{}{figures/TankTreadingFigs_composite_SCp55.pdf}
%  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
%  0cm,clip=true]{}{figures/TankTreadingFigs_composite_MCp5.pdf}
  \caption{\label{fig:lubricationComposite} \small The lubrication layer
  thicknesses (red and blue), excess pressure (green), and
  tank-treading velocity of four Lagrangian points of a (a) stiff
  single-component vesicle, (b) floppy single-component vesicle, and (c)
  multicomponent vesicle. The reduced area is $\alpha = 0.4$ in all
  three cases. 
  \textcolor{blue}{
  Also illustrated is the vesicle shape when its center of mass is
  located at $x=4$. The color represents the spread of the tangential
  velocity relative to the average tangential velocity, where the
  average is taken over the region $x \in [4,10]$. We characterize the
  stiff single-component and multicomponent vesicles as tank treading
  since the spread in the tangential velocity is below 15\%, while the
  floppy single-component vesicle is not tank treading.
  }
%  Also illustrated is the vesicle shape and the four
%  Lagrangian points at the location indicated by the dash line.
  The black dashed line is the center line of the channel, and the arrow
  denotes the tank-treading direction. The percentage of the vesicle
  membrane that is below the center line is (a) 72\%, (b) 44\%, and (c)
  68\%.}
\end{figure*}

@@

Another difference between the two reduced areas is that the vesicles
with smaller reduced area undergo tank-treading motions. As mentioned
earlier, tank-treading occurs when the top and bottom lubrication layers
differ in size. The size of the lubrication layers for all three cases
of the vesicle with reduced area $\alpha = 0.4$ are in the top half of
Figure~\ref{fig:lubricationComposite}. 
%The bottom of Figure~\ref{fig:lubricationComposite} shows the
%tank-treading velocities of four Lagrangian points. The inset shows the
%vesicle configuration in the closely-fitting part of the channel, the
%black dashed line is the center line of the channel, the marks are the
%four Lagrangian points, and the rounded arrow denotes the direction of
%rotation. 
\textcolor{blue}
{
To determine if a vesicle is tank-treading, we first calculate the
average, maximum, and minimum tangential velocities over all $N$
Lagrangian points when the vesicle's center of mass is in the interval
$[4,10]$. If the difference of the maximum and minimum tangential
velocities is within 15\% of the average tangential velocity, we
characterize the vesicle as tank-treading. These relative spreads are
plotted in the bottom row of Figure~\ref{fig:lubricationComposite}. The
average tangential velocities are $-1.00 \times 10^{-1}$ for the stiff
single-component vesicle, $3.31 \times 10^{-2}$ for the floppy
single-component vesicle, and $-8.48 \times 10^{-1}$ for the
multicomponent vesicle. The difference of the maximum and minimum
velocities relative to the average tangential velocities is $1.2\%$ for
the stiff single-component vesicle, $12\%$ for the multicomponent
vesicle, and over $300\%$ for the floppy single-component vesicle.
Therefore, we classify the stiff single-component and multicomponent
vesicles as tank treading, while the floppy single-component is not tank
treading.}
%The stiff single-component and multicomponent vesicles are
%clearly tank treading.
The direction and speed of the tank-treading depends on how much of the
vesicle membrane is exposed to positive shear (below the center line)
versus how much is exposed to negative shear (above the center
line)~\cite{kao-bir-mis2009}. The majority of the membrane of the stiff
single-component and multicomponent vesicles are below the center line,
and this results in a clockwise tank-treading behavior. In contrast, the
majority of the membrane of the floppy single-component vesicle is above
the center line, and the result is counterclockwise 
\textcolor{blue}{
rotation, but, again, large normal deformations are occuring along with
the rotation.
%}
%tank-treading. 
%\textcolor{blue}{
Finally, the stiff single-component vesicle tank treads faster than the
multicomponent cases since more of its membrane is located below the
center line.
}
%In addition, the tank-treading velocity can be correlated to the
%percentage of its membrane that is below the center line. 
%We note, however, that the floppy single-component vesicle is still
%undergoing deformations, so the tangential velocities have not converged
%to a fixed value.

The sizes of the top and bottom lubrication layers are also related to
the excess pressure. The green curve on the top half of
Figure~\ref{fig:lubricationComposite} shows the excess pressure (with
the axis aligned on the right side of the plot). 
\textcolor{blue}{
As a general trend, the sum of the top and bottom lubrication layer
thicknesses is correlated with the magnitude of the excess
pressure---larger lubrication layers correspond to smaller (less
negative) excess pressures. This is because smaller excess pressure is
required to push the same amount of fluid around the vesicle when the
lubrication layer thickness is larger.}
%As a general trend, we expect that if the total lubrication layer
%thickness---namely the sum of the top and bottom lubrication layers---is
%largest, then less pressure is required to maintain the constant flow
%rate, and the result is a smaller (less negative) excess pressure. This
%trend is confirmed in Figure~\ref{fig:lubricationComposite} where the
%size of the lubrication layers, from smallest to largest, are the stiff
%single-component vesicle, the floppy single-component vesicle, and the
%multicomponent vesicle, while the ranking of the excess pressure is
%reversed.}
%When the lubrication layers are large, most notably for the
%multicomponent vesicle, less pressure is required to force the vesicle
%through the geometry, and the result is a smaller (less negative)
%excess pressure. In contrast, when the lubrication layers are small,
%most notably for the stiff single-component vesicle, more pressure is
%required to force the vesicle through the geometry, and we the result
%is a larger (more negative) excess pressure.
